\chapter{The Database Sub-Project: PostgreSQL Schema and C\# Browser}

\section{Background}

The \textit{docs/databaseproject} directory contains a formally designed relational database model built on PostgreSQL and an ASP.NET Core / C\# database browser application. This sub-project has dual value: it strengthens the academic database-design dimension of the thesis and provides a real, runnable tool for browsing analytic results.

\section{The Formal Relational Schema}

\textit{docs/databaseproject/schema.sql} defines a complete PostgreSQL schema. The schema's ten main tables:

\begin{table}[H]
\centering
\caption{Tables of the databaseproject PostgreSQL schema}
\begin{tabularx}{\textwidth}{|>{\raggedright\arraybackslash}p{4.5cm}|X|}
\hline
\textbf{Table} & \textbf{Role in the schema} \\
\hline
\textit{players} & Player identity, aggregated scores, role \\
\textit{matches} & Match-level data: queue, patch, duration, winner \\
\textit{teams} & The two teams of a match: side and objective data \\
\textit{match\_participants} & Participant data: champion, lane, kills, deaths, assists \\
\textit{player\_relationships} & Player--player ally/enemy connection with weight \\
\textit{clusters} & Cluster metadata: type, algorithm \\
\textit{cluster\_members} & Membership records with role summaries \\
\textit{analysis\_runs} & Metadata for analysis runs \\
\textit{performance\_snapshots} & Player performance snapshots per run \\
\textit{path\_queries} & Pathfinding requests and results \\
\hline
\end{tabularx}
\end{table}

The sections covering views, stored procedures, and triggers can be found in chapter 12 of the extended version \cite{premadegraph-full}.

\section{The ASP.NET Core / C\# Database Browser}

The browser was built to browse the Premade Graph SQLite databases. On startup, the \textit{ProjectImporter.Import()} process imports the players, clusters, cluster\_members, and replay tables from the main system database. The browser reads the repository's \textit{datasets.json} registry, and the desired dataset identifier can be passed as a URL parameter (\textit{?dataset=flexset}, \textit{?dataset=soloq}).

The browser operates with server-side HTML generation and no JavaScript frontend. The \textit{Microsoft.Data.Sqlite} NuGet package provides database access. The application compiles and runs from the repository.

\section{The Sub-Project's Place in the System}

The databaseproject is not a paper exercise: \textit{schema.sql} is runnable, and the C\# browser compiles and runs. The SQLite-based main system is optimised for graph construction, analytics, and demo-pipeline serving; the PostgreSQL-based model aligns with the academic requirements of relational database design. The two serve different purposes within the same domain.
